\begin{thebibliography}{99.}

\bibitem{amsallem2008}
D Amsallem and C Farhat. Interpolation method for adapting reduced-order models and application to aeroelasticity. AIAA journal, 46(7):1803–1813, 2008.


\bibitem{barnett2022quadratic}
  Barnett, Joshua and Farhat, Charbel,
  Quadratic approximation manifold for mitigating the Kolmogorov barrier in nonlinear projection-based model order reduction, Journal of Computational Physics, {\bf 464}, (2022) pp 111348

\bibitem{barnett2023}
Barnett, Joshua, Charbel Farhat, and Yvon Maday, Neural-network-augmented projection-based model order reduction for mitigating the Kolmogorov barrier to reducibility, Journal of Computational Physics {\bf 492} (2023) pp 112420.


\bibitem{EIM2004}
Barrault, Maxime, Yvon Maday, Ngoc Cuong Nguyen, and Anthony T. Patera. An ‘empirical interpolation’method: application to efficient reduced-basis discretization of partial differential equations. Comptes Rendus Mathematique 339, no. 9 (2004): 667-672.



\bibitem{curse}
Biau, Gérard, Analysis of a random forests model, The Journal of Machine Learning Research, Volume 13 Issue 1 1063-1095, 2012

\bibitem{cagniart2019}
Cagniart Nicolas, Maday Yvon, and Stamm Benjamin. Model order reduction for problems with
large convection e ects. In Contributions to Partial Di erential Equations and
Applications, pages 131-150. Springer, 2019.

\bibitem{carlberg2015}
K Carlberg. Adaptive h-refinement for reduced-order models. International Journal for Numerical Methods in Engineering, 102(5):1192-1210, (2015).

\bibitem{cohen2009}
Cohen, Albert, Wolfgang Dahmen, and Ronald DeVore. Compressed sensing and best $k$-term approximation. Journal of the American mathematical society 22, no. 1 (2009): 211-231.
Harvard	


\bibitem{cohen2023nonlinear}
Cohen, Albert, Farhat, Charbel, Maday, Yvon and Somacal, Agustin, Nonlinear compressive reduced basis approximation for PDE’s, Comptes Rendus. M{\'e}canique, {\bf 351}-S1, pp 1--18, (2023)


\bibitem{devoreActa98}
DeVore, Ronald A. Nonlinear approximation. Acta numerica 7 (1998): 51-150.
Harvard	


\bibitem{devoreActa21}
DeVore, Ronald, Boris Hanin, and Guergana Petrova. Neural network approximation. Acta Numerica 30 (2021): 327-444.
Harvard	




\bibitem{eftang2011}
Jens L Eftang, David J Knezevic, and Anthony T Patera. An “hp” certified reduced
basis method for parametrized parabolic partial differential equations. Mathematical
and Computer Modelling of Dynamical Systems, 17(4):395–422, 2011.

\bibitem{etter2019}
Etter, Philip A., and Kevin T. Carlberg. "Online adaptive basis refinement and compression for reduced-order models via vector-space sieving." Computer Methods in Applied Mechanics and Engineering 364 (2020): 


\bibitem{ferrero2022}
Ferrero, Andrea, Tommaso Taddei, and Lei Zhang. "Registration-based model reduction of parameterized two-dimensional conservation laws." Journal of Computational Physics 457 (2022): 111068.


\bibitem{Fresca2021}
Fresca, Stefania, Luca Dedé, and Andrea Manzoni, A comprehensive deep learning-based approach to reduced order modeling of nonlinear time-dependent parametrized PDEs, Journal of Scientific Computing {\bf 87} (2021) pp. 1-36.

\bibitem{Geelen2023}
Geelen, Rudy, Stephen Wright, and Karen Willcox. Operator inference for non-intrusive model reduction with quadratic manifolds. Computer Methods in Applied Mechanics and Engineering 403 (2023): 115717.



\bibitem{bookCrb}
Hesthaven, Jan, Rozza, Gianluigi and Stamm, Benjamin, Certified Reduced Basis Methods for Parametrized Partial Differential Equations (2016)


\bibitem{iollo2014}
Angello Iollo and Damiano Lombardi. Advection modes by optimal mass transfer. Physical Review E, 89(2):022923, 2014.



\bibitem{Lee2020}
Lee, Kookjin, and Kevin T. Carlberg, Model reduction of dynamical systems on nonlinear manifolds using deep convolutional autoencoders,  Journal of Computational Physics {\bf 404} (2020), pp 108973.

\bibitem{kashima2016}
K Kashima. Nonlinear model reduction by deep autoencoder of noise response data. In 2016 IEEE 55th Conference on Decision and Control (CDC), pages 5750–5755. IEEE, 2016.

\bibitem{Kramer2024}
Kramer, Boris, Benjamin Peherstorfer, and Karen E. Willcox. "Learning nonlinear reduced models from data with operator inference." Annual Review of Fluid Mechanics 56 (2024): 521-548.


\bibitem{maday2013}
Maday, Yvon, and Benjamin Stamm. Locally adaptive greedy approximations for anisotropic parameter reduced basis spaces. SIAM Journal on Scientific Computing 35, no. 6 (2013): A2417-A2441.


\bibitem{mojgani2017}
Rambod Mojgani and Maciej Balajewicz. Arbitrary Lagrangian Eulerian framework for efficient projection-based reduction of convection dominated nonlinear ows. In APS Division of Fluid Dynamics Meeting Abstracts, 2017.

\bibitem{ohlberger2013}
Mario Ohlberger and Stephan Rave. Nonlinear reduced basis approximation of parameterized evolution equations via the method of freezing. Comptes Rendus Mathematique, 351(23-24):901{906, 2013}.

\bibitem{peherstorfer2020}
B Peherstorfer. Model reduction for transport-dominated problems via online adaptive bases and adaptive sampling. SIAM Journal on Scientific Computing 42, no. 5 (2020): A2803-A2836.


\bibitem{sklearn}
Pedregosa et al., Scikit-learn: Machine Learning in Python, JMLR 12, pp. 2825-2830, 2011

\bibitem{feelpp}
Prud'homme, Christophe et al. (2024). feelpp/feelpp: Feel++ V111 preview 9. Zenodo. https://zenodo.org/records/10837178

\bibitem{rbpp}
Prud’homme, Christophe, Rovas, Dimitrios, Veroy, Karen, Machiels, Luc, Maday, Yvon, Patera Anthony T. and Turinici Gabriel, Reliable Real-Time Solution of Parametrized Partial Differential Equations: Reduced-Basis Output Bound Methods 
 J. Fluids Eng. Mar 2002, 124(1): 70-80

  
\bibitem{bookRb}
Quarteroni, Alfio, Manzoni, Andrea and Negri, Federico, Reduced basis methods for partial differential equations: An introduction (2015), pp 1-263.

\bibitem{Taddei2015} Tommaso Taddei, Simona Perotto, and Alfio Quarteroni. Reduced basis techniques for nonlinear conservation laws. ESAIM: Mathematical Modelling and Numerical Analysis, 49(3):787{814, 2015.

\bibitem{polack2021}
Polack, Étienne, Geneviève Dusson, Benjamin Stamm, and Filippo Lipparini. "Grassmann extrapolation of density matrices for Born–Oppenheimer molecular dynamics." Journal of Chemical Theory and Computation 17, no. 11 (2021): 6965-6973.


\bibitem{Taddei2020} Tommaso Taddei. A registration method for model order reduction: data compression and geometry reduction. SIAM Journal on Scientific Computing, 42(2):A997–A1027, 2020

\bibitem{Youngkyu2020}
Kim, Youngkyu, Youngsoo Choi, David Widemann, and Tarek Zohdi. "Efficient nonlinear manifold reduced order model." arXiv preprint arXiv:2011.07727 (2020).

\bibitem{zimmermann2018}
R Zimmermann, B Peherstorfer, and K Willcox. Geometric subspace updates with applications to online adaptive nonlinear model reduction. SIAM Journal on Matrix Analysis and Applications, 39(1):234–261, 2018.



\end{thebibliography}